\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Serhan,
    middleinitial=,
    lastname=Yilmaz,
    email=serhan.yilmaz@sabanciuniv.edu,
    phone=+90 (543) 798 81 34,
    linkedin=yilmaz-serhan,
    github=serhanylmz,
    city=,
    state=,
    qrcode=,
    fixobjectivespacing=true
]

\objective{A CS student with a focus on NLP, Machine
    Learning and AI with many years of work and research
    experience around the world seeking opportunities to develop
    NLP and Computer Vision applications at NVIDIA.}

% ----- Education -----
\section{Education}

\experience{Bachelor of Science}{Computer Science}{Sep 2021}{Jun 2025}{
    \noindent Sabanci University \hfill cGPA: \textbf{3.62}/4
    \achievement{
        \textbf{\textit{Relevant Coursework:}} Machine Learning, Digital Image Processing, Linear Algebra, Statistics, Discrete Math, Algorithms, Data Structures, Advanced Programming, Operating Systems, Database Systems
    }
    \achievement{
        Ranked \textbf{top 0.02\%} among 2.9 million students in the National University Entrance Exam.
    }
}

% ----- Work Experience -----
\section{Work Experience}

\experience{Research Assistant}{Carnegie Mellon University}{Dec 2023}{Present}{
    \achievement{
        Working with Prof. Kemal Oflazer on developing advanced question generation and paraphrasing algorithms.
    }
    \achievement{
        Developing refined training methods with feedback signals for semantic understanding in paraphrasing.
    }
    \achievement{
        Employing transfer learning techniques to fine-tune T5 and BERT models for an encoder-decoder architecture.
    }
    \achievement{
        Achieved 91\% accuracy in generating high-quality, diverse research questions from input data.
    }
    \achievement{
        Evaluated generated questions using metrics like BLEU and METEOR, scoring in the top 10\% compared to existing benchmarks.
    }
}

\experience{Part-Time NLP R\&D Engineering Intern}{Yapi Kredi Bank}{Oct 2023}{Present}{
    \achievement{
        Improving document interpretation algorithms with OCR-free Donut Transformers.
    }
    \achievement{
        Fine-tuned BERT and BERTurk language models, cutting annotation effort through transfer learning techniques.
    }
    \achievement{
        Worked with cross-functional teams to translate business requirements into effective NLP solutions.
    }
}

\experience{Club Founder/President}{kAi Sabanci}{Mar 2023}{Present}{
    \achievement{
        Founded, led, and grew kAi Sabanci, Sabanci University's AI and ML club, attracting \textbf{600+ members with 80\% participation rate} in under 1 year.
    }
    \achievement{
        Organized workshops and served as a voluntary TA, delivering sessions from NVIDIA DLI in Gen AI, NLP, Conversational AI, Machine Learning, Deep Learning and CUDA with instructors from around the world.
    }
    \achievement{
        Developed and managed several key projects in collaboration with academic faculty including the \href{https://kaisabanci.com/}{ \textbf{\textit{\underline{kAi Sabanci website}}}}, our RAG-enabled Chatbot -ChatSU- as a service, 3D campus modeling with NeRF and campus cat identification with Jetson Nano.
    }
    \achievement{
        Organized panels on the AI revolution and transformation across the industry and academia, with notable guests from Stanford, Caltech, NVIDIA including \textbf{Simon See}.
    }
    \achievement{
        Held watchparties and gatherings for international developer conferences including GTC.
    }
    \achievement{
        Got kAi to become the \textbf{first} member of the \textbf{NVIDIA Student Network} in Europe. Received content \& material support from NVIDIA, \textbf{met with Jensen Huang in Stockholm.}
    }
    \achievement{
        \textbf{Selected for the NVIDIA Student Spotlight series} for outstanding perseverance, dedication and achievement.
    }
}


\experience{Summer@EPFL Intern}{EPFL - École Polytechnique Fédérale de Lausanne}{Jun 2023}{Sep 2023}{
    \achievement{
        Optimized gradient aggregation functions using PyTorch and CUDA to work up to 2200\% faster.
    }
    \achievement{
        Restructured the ML pipeline, added more functionality and modulized the code.
    }
    \achievement{
        Published a Python library for high-performance Distributed \& Federated ML applications.
    }
    \achievement{
        Created a Webpage with Flask backend to publish benchmarking leaderboards.
    }
}

\experience{Undergraduate Teaching Assistant}{Sabanci University}{Sep 2022}{Jan 2023}{
    \achievement{
        Wrote homework assignments for students and held weekly recitation and office hours.
    }
}

\experience{Undergraduate Research Assistant}{Boston University}{Jun 2022}{Sep 2022}{
    \achievement{
        Studied Threat Modeling and Component Design for large-scale server systems under the supervision of Prof. Rabia Tugce Yazicigil.
    }
    \achievement{
        Developed a helper tool using C++ which provided up to 336 different combinations to design secure servers for resource-intensive applications.
    }
}

\experience{Intern}{Pharus Tech}{Jul 2020}{Sep 2020}{
    \achievement{
        Explored data from the ESCO dataset, including 3008 occupations and 13890 skills.
    }
    \achievement{
        Visualized data relating to skill sets required for jobs using Pandas and NumPy.
    }
}

\experience{Undergraduate Research Assistant}{Koc University}{Jun 2020}{Jul 2020}{
    \achievement{
        Worked with Prof. Hakan Urey to train a machine learning model with TensorFlow on a dataset of \textbf{600} retinal images for cataract detection.
    }
    \achievement{
        Wrote a comprehensive final report and delivered a presentation about the project's methodology and findings.
    }
}

% ----- Awards -----
\section{Awards}
\experience{NVIDIA Student Spotlight}{NVIDIA}{Mar 2023}{Present}{
    \achievement{
        Selected for the NVIDIA Student Spotlight series for outstanding perseverance, dedication and achievement.
    }
}
\experience{Sakip Sabanci Award for Outstanding Success}{Sabanci University}{Sep 2022}{Present}{
    \achievement{
        Ranked \textbf{top 4\%} among the students in my term.
    }
}
\experience{Innovation in Crisis}{The Royal Swedish Academy of Engineering Sciences}{May 2020}{Present}{
    \achievement{
        Young Innovation in Times of Crisis Award for ranking in the \textbf{1st place} among all projects.
    }
}
\experience{Membership Award}{The New York Academy of Sciences}{Sep 2019}{Present}{
    \achievement{
        Young Member of the New York Academy of Sciences Award for admission into "The Junior Academy" program with an acceptation rate of
        \textbf{8\%}.
    }
}

% ----- Projects -----
\section{Projects}

\experience{Combating Covid-19}{New York Academy of Sciences}{Jan 2020}{May 2020}{
    \achievement{
        Developed and visualized an algorithm to match job seekers with job providers in the Covid-19 outbreak.
    }
    \achievement{
        \textbf{Awarded 1st Place} by the Royal Swedish Academy of Engineering Sciences.
    }
}

\experience{Advanced Question Generation and Paraphrasing}{Carnegie Mellon University}{Dec 2023}{Present}{
    \achievement{
        Worked with Prof. Kemal Oflazer to develop algorithms for generating and paraphrasing research questions.
    }
    \achievement{
        Employed transfer learning techniques to fine-tune T5 and BERT models, achieving 91\% accuracy in generating diverse questions.
    }
}

\experience{Project Charisius for Federated ML}{EPFL Lausanne}{Jun 2023}{Sep 2023}{
    \achievement{
        Optimized gradient aggregation functions using PyTorch and CUDA for a speed increase of up to 2200\%.
    }
    \achievement{
        Restructured the ML pipeline for added functionality and modularity.
    }
    \achievement{
        Published a Python library for distributed and federated ML applications.
    }
}

\experience{Project Sanity Check}{Sabanci University}{Feb 2023}{May 2023}{
    \achievement{
        Developed an education index for all provinces of Turkey using machine learning to measure the expected education indices for the year 2020.
    }
    \achievement{
        Compared the predicted indices with the actual education index from 2020 to assess the impact of the Covid-19 pandemic on education in different Turkish provinces.
    }
    \achievement{
        Presented the index and results on an interactive, online map, providing a visual representation of the pandemic's effect on education across Turkey.
    }
}

\experience{Cataract Detection using Machine Learning}{Koc University}{Jun 2020}{Jul 2020}{
    \achievement{
        Trained a machine learning model with TensorFlow on a dataset of 600 retinal images for cataract detection.
    }
    \achievement{
        Delivered a comprehensive final report and presentation on the project's methodology and findings.
    }
}

\experience{NeRF Project at Sabanci University (NERFSU)}{kAi Sabanci}{Sep 2023}{Present}{
    \achievement{
        Led an ambitious project to create a detailed 3D digital model of Sabanci University's campus using Neural Radiance Fields (NeRF) and advanced AI/ML algorithms.
    }
    \achievement{
        Analyzed a vast collection of high-resolution photographs from various angles to extract visual details and structural information.
    }
    \achievement{
        Employed the NeRF algorithm to infer the underlying 3D structure, resulting in an immersive and realistic representation of the university for virtual exploration and interactive experiences.
    }
}

\experience{Parking Spot Detection}{kAi Sabanci}{Apr 2023}{June 2023}{
    \achievement{
        Developed a computer vision-based system for real-time detection and classification of parking spots using deep learning algorithms.
    }
    \achievement{
        Utilized convolutional neural networks (CNNs) and advanced image processing techniques to analyze live video feeds from parking lot cameras.
    }
    \achievement{
        Applied object detection and classification algorithms to accurately identify and track vehicles within the parking premises, aiming to revolutionize parking management and improve overall parking efficiency.
    }
}

\experience{ChatSU Implementation}{kAi Sabanci}{Mar 2023}{Present}{
    \achievement{
        Implemented ChatSU, a chat generative AI powered by GPT-4, into a website to converse with visitors and respond to their queries using natural language.
    }
    \achievement{
        Integrated the AI system into the website's backend and frontend, allowing for seamless interaction through a chat window.
    }
    \achievement{
        Planned future improvements, including training a text-to-speech model for ChatSU to speak responses and a speech-to-text model to enable voice-based conversations with users.
    }
}

\section{Skills}

\achievement{
    \textbf{Languages \& Tools:} \tech{Python}, \tech{Java}, \tech{Javascript}, \tech{HTML/CSS}, \tech{C}, \tech{C++}, \tech{Docker}, \tech{Linux}
}
\achievement{
    \textbf{Libraries:} \tech{PyTorch}, \tech{TensorRT}, \tech{JAX},
    \tech{PyTorch Lightning}, \tech{TensorFlow}, \tech{OpenCV}, \tech{CUDA},
    \tech{OpenGL}, \tech{NumPy}, \tech{Pandas}, \tech{Keras},
    \tech{Flask}, \tech{React}
}

\end{document}